\documentclass[final,twoside]{vutinfth}

% Core thesis metadata.
\newcommand{\authorname}{Denys Nahornyi}
\newcommand{\thesistitleen}{Economically secure 2PC on Ethereum}
\newcommand{\thesistitlede}{Economically secure 2PC on Ethereum}
\newcommand{\curriculumen}{Master's programme Software Engineering \& Internet Computing}
\newcommand{\curriculumde}{Masterstudium Software Engineering \& Internet Computing}
\newcommand{\thesistitle}{\thesistitleen}

% PDF/A metadata block.
\begin{filecontents*}[overwrite]{\jobname.xmpdata}
\Author{\authorname}
\Title{\thesistitle}
\Language{en-US}
\Keywords{privacy-preserving auctions\sep secure two-party computation\sep Ethereum\sep smart contracts}
\Publisher{TU Wien}
\Subject{Master Thesis}
\end{filecontents*}

% UTF-8 input and modern font output.
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{listings}
\usepackage[ruled,linesnumbered,algochapter]{algorithm2e}
\usepackage[a-2b,mathxmp]{pdfx}
\usetikzlibrary{arrows.meta,positioning}
\lstdefinestyle{soliditysnippet}{
  basicstyle=\ttfamily\footnotesize,
  columns=fullflexible,
  breaklines=true,
  keepspaces=true,
  showstringspaces=false,
  frame=single
}
% Keep hierarchy readable: number down to subsections only.
\setsecnumdepth{subsection}
\settocdepth{subsection}

% Required persons.
\setauthor{}{\authorname}{}{male}
\setadvisor{Assistant Prof.}{Georgia Avarikioti}{Dr.sc.ETH}{female}

% Participation field on title page (assistant involved).
\setfirstassistant{}{Ioannis Alexopoulos}{}{male}

% Required thesis data.
\setregnumber{11742819}
\setdate{10}{05}{2026}
\settitle{\thesistitleen}{\thesistitlede}
\setthesis{master}
\setmasterdegree{dipl.}
\setcurriculum{\curriculumen}{\curriculumde}

\begin{document}

\frontmatter

% Front matter order follows paper/EXAMPLE/example.tex.
\addtitlepage{naustrian}
\addtitlepage{english}
\addstatementpage{english}

\begin{acknowledgements*}
I would like to express my sincere gratitude to my supervisor, Assistant Prof.
Georgia Avarikioti, for her guidance, insightful feedback, and continuous
support throughout this thesis.

I am especially grateful to Ioannis Alexopoulos for his valuable discussions on
protocol design, as well as for his thoughtful feedback and practical guidance
during the implementation and evaluation phases. His input not only improved
the technical quality of this work but also helped shape its overall direction.

Finally, I would like to thank my family for their unwavering emotional and
material support, without which this work would not have been possible. I am
equally grateful to my friends for their encouragement, patience, and
inspiration throughout this journey. I also want to thank my girlfriend, Maria,
for her love, understanding, and constant support throughout this process.
\end{acknowledgements*}

\begin{kurzfassung}
Diese Arbeit untersucht, wie wirtschaftlich sichere Zwei-Parteien-Berechnung
(2PC) auf Ethereum für private Gebotsprotokolle umgesetzt werden kann. Der
Ausgangspunkt ist ein zentrales Spannungsfeld öffentlicher Blockchains:
Transparenz erhöht die Nachvollziehbarkeit, begünstigt aber zugleich
strategisches Verhalten durch sichtbare Transaktionen und Reihenfolgeeffekte.
Für versiegelte Auktionen führt dies zu einer direkten Herausforderung für
Fairness, Vertraulichkeit und Durchsetzbarkeit.

Die Forschungsfrage lautet, wie ein Protokoll gestaltet werden kann, das
gleichzeitig (i) Eingabeprivatheit der Gebote, (ii) öffentlich überprüfbare
Durchsetzung, (iii) Robustheit gegenüber Verzögerung und Abbruch sowie
(iv) praktische Umsetzbarkeit unter Ethereum-Randbedingungen erreicht.
Methodisch kombiniert die Arbeit ein Off-Chain-2PC-Design auf Basis von
Garbled Circuits und Oblivious Transfer mit einer On-Chain-Statusmaschine.
Der Smart Contract erzwingt Phasenübergänge, Commitments, Deadlines,
Dispute-Pfade und deterministische Settlement-Regeln.

Als Ergebnis wurde ein Proof-of-Concept in Solidity und Rust implementiert und
in End-to-End-Szenarien evaluiert (ehrlicher Ablauf, Evaluator-Default,
Garbler-Cheating). Die Evaluation zeigt, dass
Anchor-gebundenes Settlement, begrenzte aber öffentliche
Verifizierbarkeit über explizite Dispute-Prädikate sowie Liveness durch
Default-/Slashing-Mechanismen in einer konsistenten Ausführungslogik kombiniert
werden können. Damit wird gezeigt, dass ökonomisch sichere 2PC auf Ethereum im
Protokollkern praktisch realisierbar ist. Als Anwendungsschicht wird eine
ENS-Auktionsabbildung demonstriert. Die Arbeit grenzt zugleich klar ab, dass
vollständige Gas-Kalibrierung unter Produktionsbedingungen und weitergehende
ökonomische Parametersynthese zukünftige Arbeiten sind.
\end{kurzfassung}

\begin{abstract}
In this thesis, we examine how economically secure two-party computation (2PC)
can be realized on Ethereum for private bidding protocols. The motivating
tension is structural: public-chain transparency supports auditability, yet the
same visibility exposes transaction data and ordering opportunities that can
distort fairness and correctness in sealed-bid execution.

Our central question is whether one protocol can preserve bid privacy until
valid settlement, remain publicly enforceable, tolerate strategic delay or
abort behavior, and still be practically deployable under Ethereum constraints.
To address this, we combine off-chain garbled-circuit/OT execution with an
on-chain enforcement state machine. The contract governs phase transitions,
commitments, deadlines, dispute entry points, and deterministic settlement
rules.

Our implementation delivers a Solidity+Rust proof of concept, evaluated in
end-to-end scenarios: an honest run, an evaluator-defaulted liveness path, and
a garbler-cheat dispute path. We observe that structured output-anchor binding,
selective publicly verifiable dispute predicates, and
deadline-based default/slashing logic can be integrated into a single coherent
protocol flow. This supports the practical feasibility of economically secure
2PC on Ethereum at the protocol-core layer. We further implement an ENS auction
mapping as an application layer over the same enforcement backbone.

We also state clear boundaries: full production-grade gas calibration and
deeper economic parameter optimization remain future work.
\end{abstract}

\selectlanguage{english}
\tableofcontents

\mainmatter

\chapter{Introduction}
\section{Context and Motivation}
Public blockchains provide strong auditability, but that property comes with a direct tradeoff: transaction data and transaction ordering are visible before final settlement. On Ethereum, this transparency enables adversarial strategies such as reordering, insertion, and censorship, often discussed under maximal extractable value (MEV)~\cite{Wood2025Ethereum,Daian2019FlashBoys}. For protocols with private inputs, this visibility is not a side issue; it directly affects fairness and correctness.

Sealed-bid auctions make this tension concrete. Bids should remain private during execution, while the final winner and settlement must still be publicly enforceable. If private information leaks too early, strategic behavior can distort the outcome and reduce trust in the mechanism. If enforcement is weak, parties can deviate or abort at points where deviation is economically beneficial.

Recent work by Alexopoulos et al. (BitPriv) shows that privacy-preserving and economically enforceable computation can be achieved in a Bitcoin-native environment through off-chain two-party computation (2PC), collateral-backed incentives, and on-chain dispute resolution~\cite{BitPriv2025}. Building on that direction, this thesis addresses Ethereum directly and develops a protocol and prototype tailored to Ethereum execution constraints, with explicit state-machine enforcement, scoped disputes, and deterministic settlement rules.

\section{Problem Statement}
The central challenge is to design a protocol for sealed-bid auctions on Ethereum that satisfies four properties simultaneously:
\begin{enumerate}
\item \textbf{Input privacy}: bids are not revealed before the protocol reaches a valid settlement point.
\item \textbf{Public enforceability}: the on-chain contract can enforce the agreed output and financial transfers.
\item \textbf{Robustness to strategic behavior}: the protocol remains operational when parties stall, abort, or provide inconsistent artifacts.
\item \textbf{Practical deployability}: on-chain overhead remains manageable and implementation complexity stays within realistic engineering bounds.
\end{enumerate}

In public-blockchain deployments, these goals interact in non-trivial ways. Stronger cryptographic guarantees may increase operational cost, while cheaper constructions can weaken deterrence against rational deviations. The design therefore has to be reasoned about not only cryptographically, but also economically: the expected payoff of honest behavior should dominate profitable deviation under explicit assumptions~\cite{Zhu2019PV2PC}.

Accordingly, this thesis follows an \emph{optimistic, dispute-driven enforcement} model.
On-chain logic enforces deadlines, deposits, slashing, settlement-anchor checks,
and selective dispute predicates, where dispute handling includes bounded,
selective on-chain GC/OT checks via partial recomputation/verification of
challenged steps. Off-chain logic performs the full GC/OT evaluation and
derives \texttt{outputBytes}. In this split, on-chain logic enforces binding,
deadlines, and accountable state transitions, while computational integrity is
established through deterministic off-chain execution and dispute evidence.

\section{Research Objectives}
Following the approved thesis proposal, the objective is to design and prototype an economically secure 2PC protocol for Ethereum-based sealed-bid auctions, with first-price auctions as the baseline use case.

Concretely, the thesis targets:
\begin{enumerate}
\item a protocol architecture that combines off-chain 2PC execution with on-chain commitments, deadlines, and disputes;
\item a threat and assumptions model suitable for adversarial transaction environments;
\item a Solidity + Rust proof-of-concept demonstrating end-to-end execution;
\item an evaluation of feasibility, including cost/performance characteristics and dispute-path practicality;
\item an economic-security analysis that explains how deposits, collateral, and penalties deter rational cheating.
\end{enumerate}

\section{Contributions of This Thesis}
The expected contributions are the following:
\begin{enumerate}
\item \textbf{Ethereum-oriented protocol design and engineering:} a protocol that preserves bid privacy while keeping settlement publicly enforceable in a hostile execution environment, using explicit phase transitions, enforceable dispute predicates, and deterministic settlement logic.
\item \textbf{Economic-security framing:} a practical incentive model for rational participants, including explicit assumptions and deterrence conditions.
\item \textbf{Prototype implementation:} an integrated proof-of-concept with on-chain contract logic and off-chain 2PC components.
\item \textbf{Empirical evidence:} implementation-driven measurements and scenario-based analysis of optimistic and dispute executions.
\end{enumerate}

\section{Thesis Structure}
The remainder of the thesis is organized as follows.
Chapter~2 first introduces the blockchain, Ethereum, EVM, ENS, and 2PC background needed for this thesis, and then positions this work relative to privacy-preserving blockchain protocols and blockchain-based auction mechanisms. Chapter~3 defines the model, assumptions, adversaries, and formalized requirements.
Chapter~4 presents the protocol design and phase-by-phase logic.
Chapter~5 describes the implementation architecture and engineering choices.
Chapter~6 evaluates the prototype with respect to cost, performance, and protocol behavior under key scenarios.
Chapter~7 discusses limitations, summarizes the main findings, and outlines future work.

\chapter{Background and Related Work}
\section{Background}

\subsection{Blockchain Basics}
\paragraph*{General Model: State-Machine Replication.}
A blockchain can be modeled as a replicated append-only state machine maintained under decentralized consensus. Nodes process transactions according to shared rules and converge to the same ordered state-transition history. This model is the systems baseline for enforceable digital agreements: transitions are globally visible, replayable, and externally verifiable from public state~\cite{Wood2025Ethereum}.

For protocol design, this abstraction is not merely conceptual. It determines what can be objectively checked by third parties, how deadlines are interpreted, and which evidence artifacts can be tied to deterministic state transitions. In this thesis, that property is essential because enforcement is delegated to on-chain state progression rather than trusted off-chain arbitration.

\paragraph*{Permissionless Blockchains: Proof of Work and Proof of Stake.}
In permissionless systems, participation does not require prior authorization, so consensus must include explicit Sybil resistance. Proof of Work (PoW) and Proof of Stake (PoS) are the main families: both target robust agreement under adversarial conditions, but differ in resource assumptions, participation dynamics, and security-economic surfaces.

These differences matter for any protocol that depends on timed commitments, transaction inclusion, and challenge windows. Finality behavior, congestion conditions, and inclusion incentives are part of the execution environment and therefore part of the effective threat model.

\paragraph*{Why Ethereum for This Thesis.}
For this thesis, the settlement layer must satisfy four practical conditions: executable enforcement logic, native asset custody, publicly verifiable state transitions, and interoperability with existing on-chain applications. Ethereum is selected because it combines these properties in a mature production ecosystem while exposing exactly the adversarial realities relevant for private auctions: mempool visibility, strategic transaction ordering, and latency asymmetries~\cite{Wood2025Ethereum,Daian2019FlashBoys,Qin2022MEV}.

The economic scale is also material for motivation. As of May~10,~2026, Ethereum accounts for roughly USD~85.5 billion in DeFi total value locked, while Ethereum-based DEX activity is approximately USD~44.9 billion over a 30-day window~\cite{DefiLlamaEthereumChain2026,DefiLlamaEthereumDexVolume2026}. This indicates that auction-relevant value and trading flow are already large enough that privacy leakage and delayed finality are practical, not purely theoretical, concerns.

The choice is therefore not ``Ethereum despite adversarial execution'' but ``Ethereum because adversarial execution must be treated as first-class design input.'' This principle guides the transition from background concepts to concrete protocol requirements in Chapter~3.

\subsection{Ethereum and the EVM}
\paragraph*{Ethereum as Settlement Layer.}
Ethereum extends the blockchain state-machine model with programmable smart contracts, enabling stateful protocol logic without a trusted intermediary~\cite{Wood2025Ethereum}. For deployment-oriented protocol engineering, four properties are central.

First, ecosystem maturity: operational tooling, wallet support, and indexing infrastructure reduce integration and observability friction. Second, composability: contracts can interact with existing on-chain assets and modules through shared state and deterministic calls. Third, economic security: settlement semantics rely on consensus-backed inclusion/finalization, not only local contract code correctness. Fourth, public accountability: all contract-visible transitions (commitment publication, timeout progression, dispute outcomes, payouts) are externally auditable.

Together, these properties match the objective of economically secure private computation: confidentiality-critical work can remain off-chain, while enforcement remains transparent and objective on-chain.

\paragraph*{EVM Constraints and Gas-Driven Architecture.}
Smart contracts execute in the Ethereum Virtual Machine (EVM), a deterministic bytecode runtime replicated by validators. Deterministic replication is the technical basis for public enforceability: all validators must reach the same post-state from the same pre-state and transaction input.

At the same time, the EVM imposes strong practical constraints. Execution is gas-priced, storage writes are expensive, and data-heavy verification scales poorly. Full transcript re-execution is therefore not a practical default behavior for large cryptographic artifacts. In addition, calldata/storage/state transitions are public, which rules out native confidential in-contract execution as a baseline approach.

These constraints motivate the architecture adopted in this thesis:
\begin{enumerate}
\item execute heavy private computation off-chain;
\item keep on-chain logic focused on commitments, deadlines, and bounded checks;
\item rely on selective dispute predicates for accountability instead of universal on-chain recomputation.
\end{enumerate}

Data publication strategy is part of the same constraint set. If settlement references large off-chain artifacts, publication and availability pathways influence cost and liveness assumptions. EIP-4844 blob transactions are therefore directly relevant for practical deployment analysis~\cite{Buterin2022EIP4844}.

\subsection{Ethereum Name Service}
The Ethereum Name Service (ENS) maps human-readable names (for example, \texttt{alice.eth}) to Ethereum addresses and related records~\cite{EIP137ENS,ENSDocs}. Valuable names behave as scarce digital assets and are naturally allocated via market mechanisms such as auctions. Classical auction theory shows that equilibrium outcomes depend on information structure, which makes privacy properties economically material in this setting~\cite{MilgromWeber1982}.

In transparent blockchain execution, public bids leak willingness-to-pay and strategy signals. This exposes auction flows to valuation leakage, reactive bidding on partially observed information, collusion support channels, and ordering manipulation opportunities~\cite{Daian2019FlashBoys}. Hence, bid privacy is not an aesthetic feature; it is a mechanism-quality requirement.

ENS auctions are a suitable benchmark for this thesis because they require both properties simultaneously: private bid formation and publicly enforceable final allocation/payment. They also provide a clean application context for separating protocol-core guarantees from application-layer semantics.

\subsection{Secure Two-Party Computation}
\paragraph*{2PC and Garbled Circuits.}
Secure two-party computation (2PC) asks how two mutually distrustful parties can evaluate a function over private inputs while revealing only the prescribed output. The baseline adopted in this thesis follows the garbled-circuit line with oblivious transfer (OT) for input-label delivery. Foundations and formal treatments are established in classical and modern work~\cite{Bellare2012FoundationsGC,LindellPinkas2008}, while optimizations such as Half-Gates improve communication efficiency under standard security assumptions~\cite{Zahur2015HalfGates}.

In blockchain-integrated settings, this approach enables an explicit labor split: private heavy computation is handled off-chain, and chain logic focuses on commitment binding, deadline enforcement, dispute entry points, and settlement transitions.

\paragraph*{From Semi-Honest to Malicious Security.}
Semi-honest security assumes parties follow the protocol but may try to infer additional information from observed transcripts. In financial workflows, this assumption is often insufficient because profitable strategic deviation is expected. Malicious security introduces explicit safeguards such as commitment-consistency checks, cut-and-choose-style validation, and controlled abort handling~\cite{LindellPinkas2008}.

The practical tradeoff is multi-dimensional. Stronger malicious guarantees increase not only communication and verification cost, but also off-chain setup effort and end-to-end latency from setup to enforceable completion. In auction environments with moving market conditions, this latency interacts directly with economic utility, so security level and deployability must be calibrated jointly rather than optimized in isolation.

Concretely, moving toward stronger malicious security usually increases off-chain computation overhead in preparation and checking phases (for example, heavier consistency checks, larger challenge-ready evidence, and additional transcript validation work). This extra off-chain work increases latency to practical finality, understood here as the time between protocol setup and enforceable on-chain completion. For financial applications, especially auctions where external prices move continuously, this delay is not neutral: slower finality can reduce strategy quality and market relevance of the computed outcome.

\section{Related Work}

\subsection{Privacy on Blockchains}
Publicly verifiable 2PC studies how deviations can be externally validated so a smart contract or third party can arbitrate disputes without replaying full private execution. Zhu et al.\ provide a key direction for blockchain-based financially secure computation~\cite{Zhu2019PV2PC}. BitPriv extends this perspective with collateral-backed punishment and publicly verifiable dispute handling~\cite{BitPriv2025}.

A parallel line of work addresses private smart contracts on expressive blockchain platforms. Early zkSNARK-oriented frameworks such as Hawk demonstrate privacy-preserving smart-contract execution, but rely on a trusted manager role~\cite{Kosba2016Hawk}. Later decentralized private-computation frameworks such as Zexe and VeriZexe remove that manager and pursue stronger confidentiality capabilities via succinct proof systems~\cite{Bowe2018Zexe,Xiong2023VeriZexe}. This line establishes important capability frontiers, but it targets a different objective envelope than the one prioritized in this thesis.

System-oriented designs explore additional points in the tradeoff space. gcVM investigates publicly auditable MPC-compatible execution in EVM-like environments~\cite{Yanai2026gcVM}; COTI V2 studies confidentiality-oriented L2 design under extra system assumptions~\cite{Haloani2024COTIv2}. For Ethereum deployment, data publication pathways are also first-order concerns: EIP-4844 introduces blob-based publication with different availability and cost characteristics from calldata~\cite{Buterin2022EIP4844}.

Other systems expose further confidentiality/trust tradeoffs. zkay and Zapper provide privacy-oriented developer tooling and private-contract abstractions, but still leave information-leakage or anonymity-limit considerations under their operating models~\cite{zkay2019,Zapper2022}. zkHawk and its V-zkHawk follow-up reduce single-manager trust via MPC-based execution, but require stronger multi-party availability assumptions for execution/finalization~\cite{zkHawk2021,VzkHawk2022}. Eagle introduces an efficient MPC-based confidential-contract architecture with committee-style server assumptions~\cite{Eagle2023}. ZeeStar and smartFHE pursue confidentiality via homomorphic-encryption-based computation, with remaining leakage surfaces around client identity or interaction patterns depending on deployment and threat model~\cite{ZeeStar2022,SmartFHE2023}. Arbitrum-style off-chain execution and Ekiden-style TEE-backed confidential execution reduce on-chain overhead, but introduce trust in external execution components; in TEE-based settings, this includes hardware and vendor trust assumptions~\cite{Arbitrum2018,Ekiden2019}. More recent doubly-private systems such as Jigsaw target stronger goals (hiding both data and contract logic), at the cost of heavier cryptographic machinery and additional assumptions~\cite{Jigsaw2025}.

Positioning of this thesis is therefore explicit: for sealed-bid auctions on Ethereum, the target is a lighter deployment profile without zkSNARK dependency in the core enforcement path, without trusted manager roles, without external committee or system-level confidentiality assumptions, and without TEE-based execution assumptions. Accordingly, the design is intentionally lightweight: it combines off-chain 2PC with bounded on-chain commitment/dispute enforcement instead of proof-system-heavy private-contract architectures. We do not require payment unlinkability or hiding the function itself as first-class goals; the required property is bid privacy until enforceable outcome finalization. The auction function itself is public; what must remain private are the bidders' inputs until valid settlement, while correctness and accountability remain publicly enforceable. Correctness and accountability are anchored in off-chain 2PC, on-chain commitments, deadline transitions, and selective dispute predicates.

\subsection{Auctions on Blockchains}
Privacy-preserving auctions on public ledgers remain an active design area. FAST studies fair auction mechanics with secret-transaction techniques~\cite{David2021FAST}. More generally, auction behavior on transparent chains must be analyzed jointly with adversarial execution dynamics, including ordering manipulation and MEV exposure~\cite{Daian2019FlashBoys,Qin2022MEV}.

This perspective aligns with broader cryptocurrency-systems analyses, where security arguments are evaluated together with incentive compatibility and deployment constraints rather than in cryptographic isolation~\cite{Bonneau2015SoK}. For auction mechanisms, this means mechanism quality depends not only on privacy guarantees, but also on liveness behavior, enforceability under deadlines, and cost-bounded dispute handling.

Relative to this landscape, the contribution of this thesis is an implementation-coupled economic-security profile for Ethereum sealed-bid workflows: private bid computation off-chain, enforceable settlement binding on-chain, and deterrence calibration through collateral, slashing, and deadlines under realistic execution constraints.

\chapter{Model and Requirements}
\section{System Model and Roles}
The system has three layers.

\begin{enumerate}
    \item \textbf{Protocol core.}
    The protocol core coordinates one seller/garbler $G$ and $n$ buyers
    $B_1, \ldots, B_n$. They execute a private auction computation under a
    contract-enforced flow of commitments, disputes, deadlines, and settlement.

    In the implemented auction instantiation, this computation is represented by
    one global garbled circuit. The circuit has separate input-wire ranges for
    the seller and for each buyer. The seller provides the auction parameters,
    including the reserve price. Each buyer provides a private bid through
    OT-selected input labels.

    \item \textbf{Contract enforcement layer.}
    The smart contract manages deposits, deadlines, slashing, phase transitions,
    and bounded verification checks. The contract enforces the protocol, but it
    is not itself a cryptographic party.

    \item \textbf{Application instantiation.}
    The application layer maps the circuit output to ENS auction semantics. In
    this thesis, the output encodes the winner identity, the winning bid, and the
    chosen name hash. The application layer then applies assignment and payout
    rules.
\end{enumerate}

Throughout this chapter, one \emph{protocol execution} means one cut-and-choose
run over $N$ instances of the same computation circuit. One instance $m$ is
selected for evaluation.

At the protocol-core level, the computation is deterministic and the accepted
result is bound to a committed settlement anchor. In the auction instantiation
used in this thesis, the selected computation produces:
\[
\begin{array}{l}
outputBytes = F(reservePrice, bid_1, \ldots, bid_n) \\
\phantom{outputBytes} = \texttt{encodePacked}(\texttt{winnerId}, \texttt{winningBid}, \texttt{chosenNamehash}).
\end{array}
\]

Before settlement, each buyer initially knows only the selected input labels for
its own bid wires. These labels are obtained through OT. The selected input labels
of other buyers become available only in the label-availability phase, either
through cooperative off-chain exchange or through an explicit on-chain fallback
reveal.

This privacy claim assumes correct off-chain artifact handling. Operational leak
vectors such as debug logs, local storage exposure, or external telemetry are
outside the cryptographic guarantee boundary.

\section{Contract-Orchestration State Model}
The following phases describe contract orchestration for the chosen
instantiation. They are enforcement and liveness stages, not cryptographic 2PC
primitives:
\begin{enumerate}
\item deposits,
\item buyer-seed commit and reveal,
\item core commitments and buyer-scoped OT-root commitments,
\item buyer OT completion and input-label commitments,
\item cut-and-choose opening,
\item dispute window,
\item seller-side label reveal and evaluation payload binding,
\item buyer input-label availability,
\item settlement, assignment, final payout, or timeout resolution.
\end{enumerate}

For each circuit instance $i\in\{0,\dots,N-1\}$, the model includes commitment
objects such as seed commitments (`comSeed`), garbled-artifact roots
(`rootGC`), evaluation blob hashes (`blobHashGC`), buyer-scoped OT roots
(`buyerRootOTCommitment`), and output anchors (`hOut`). For the selected
evaluation instance $m$, the model additionally includes buyer input-label
commitments:
\[
\mathrm{cLabel}_j = H(\texttt{"INLABEL"},\mathrm{circuitId},m,B_j,\mathrm{inputLabels}^m_j).
\]
where $\mathrm{inputLabels}^m_j$ denotes the selected input labels received by
buyer $B_j$ for its own bid wires in instance $m$.
These commitments bind each buyer to the selected labels later used in the
cooperative/off-chain share path or on-chain fallback reveal before settlement.
The selected evaluation instance is derived from finalized verifier-seed
material, and output validity is modeled as hash binding to the committed
anchor for that instance.

The design objective is to keep high-volume cryptographic artifacts off-chain
during normal execution while preserving a scoped, externally verifiable
dispute path. This aligns with practical Ethereum deployment constraints and
data-publication tradeoffs (including blob-based publication
options)~\cite{Buterin2022EIP4844}.

\section{Adversary and Deviation Model}
The adversarial model combines:
\begin{enumerate}
\item \textbf{malicious protocol behavior} at the party level (invalid commitments, inconsistent openings, selective abort),
\item \textbf{rational economic behavior} (deviation is attempted when expected utility is positive),
\item and \textbf{adversarial transaction environment} on public Ethereum (observable mempool, reorderability, latency asymmetry)~\cite{Daian2019FlashBoys}.
\end{enumerate}

The adversary can delay, reorder, or strategically time its own transactions,
but it cannot break standard cryptographic assumptions. The contract and chain
consensus are assumed to follow Ethereum's underlying security model. In this
thesis, base-consensus denial-of-service and chain-level catastrophic failures
are out of scope.

Representative deviations considered in the model include:
\begin{enumerate}
\item submitting malformed commitments,
\item opening data inconsistent with previous commitments,
\item issuing false disputes to delay settlement,
\item withholding required messages near deadlines,
\item and attempting invalid output submission.
\end{enumerate}

\section{Assumptions}
We analyze the protocol under the following assumptions. They specify the
cryptographic guarantees, reproducibility requirements, timing model, data
availability conditions, and application-specific integration properties needed
for the protocol's security and correctness arguments.

\textbf{A1. Cryptographic assumptions.}
Hash functions used for commitments and anchors are collision-resistant, and
the underlying garbled-circuit/OT constructions provide their expected security
properties under standard
assumptions~\cite{Bellare2012FoundationsGC,LindellPinkas2008}.

\textbf{A2. Deterministic reconstruction interface.}
Given agreed seeds and domain-separation inputs, honest verifiers reconstruct
the same per-instance artifacts and transcript commitments. This assumption is
required so that disputes are objective and reproducible.

\textbf{A3. Contract-enforceable timing.}
Deadlines are represented in contract state and interpreted under Ethereum block
progression (deposit, verifier-seed, commitment, evaluator-input, open,
dispute, labels, settle windows). A party that misses a required action before
its deadline is treated as non-cooperative and penalized by protocol rules.

\textbf{A4. Data availability during dispute windows.}
Data needed for a valid challenge is available to challengers in time, either
by direct exchange or by a publication path bound to on-chain references (for
example, blob-hash anchored payloads)~\cite{Buterin2022EIP4844}.
For blob-linked publication paths, this availability assumption is scoped to the
dispute window. Blob references are treated as retrieval anchors for challenge
resolution (implementation reference: Appendix~\ref{app:a4}).

\textbf{A5. Constrained on-chain verification.}
On-chain verification is intentionally constrained to selective checks (for
example, leaf-level consistency checks), aligning verification cost with
Ethereum deployment constraints.

\textbf{A6. Instantiation assumption: ENS adapter correctness and authority.}
For the ENS application mapping, the adapter called by the contract is assumed
to be authorized to perform assignment for the offered names and to implement
\texttt{assign(namehash,to)} correctly (without hidden side paths). Detailed ENS
ownership/registration mechanics are treated as application-integration context,
not as a protocol-core security claim of this thesis.

\section{Security Requirements}
Under the above model, requirements are separated into:
\textbf{security claims for the 2PC core} (R1--R3) and
\textbf{engineering requirements for enforcement/instantiation} (R4--R6).

\textbf{R1. Input privacy.}
No party learns the counterparty's private input beyond what is implied by the
prescribed output and mandatory on-chain disclosures. This requirement follows
the BitPriv covert-2PC privacy objective and standard GC/OT security
assumptions~\cite{BitPriv2025,Bellare2012FoundationsGC,LindellPinkas2008}.

\textbf{R2. Output correctness and binding.}
An accepted settlement must correspond to a valid protocol-consistent output.
Invalid output labels or inconsistent evidence must be rejectable by the
contract. This requirement is aligned with BitPriv's enforceable-correctness
framing and grounded in standard GC/OT correctness and binding
assumptions~\cite{BitPriv2025,Bellare2012FoundationsGC,LindellPinkas2008}.
In this implementation, settlement-time checks establish anchor binding and
tuple validity, while deterministic off-chain evaluation and dispute evidence
provide computational integrity. This deployable-verification model is
deliberate and aligned with Assumption~A5. Any \texttt{outputBytes} that do not
match committed $\mathrm{hOut}_m$ are rejected by construction.
Implementation excerpts for this requirement are collected in
Appendix~\ref{app:a2} and Appendix~\ref{app:d1}.

\textbf{R3. Publicly verifiable accountability.}
When a party deviates in a way covered by dispute predicates, a challenger can
provide evidence that is verifiable by the contract (directly or through
selective verification hooks), leading to deterministic blame assignment in the
BitPriv-style accountability model~\cite{BitPriv2025,Zhu2019PV2PC}.
Implementation excerpts for dispute and slashing are collected in
Appendix~\ref{app:a3}, Appendix~\ref{app:b3}, and
Appendix~\ref{app:c1}--\ref{app:c2}.

\textbf{R4. Liveness with penalties.}
A single uncooperative party should not be able to block progress indefinitely.
If progress is blocked, timeout paths must release funds and/or apply penalties
according to predefined rules.

\textbf{R5. Application-level settlement integrity.}
Final payout execution must be unambiguous and consistent with the agreed settlement function $g(z)$.

\textbf{R6. Minimal information leakage in enforcement.}
Dispute and settlement data published on-chain should be limited to what is
necessary for enforceability.

\subsection{Proof Sketches for R1--R3}
Under Assumptions A1--A5, this thesis does not reproduce a full formal proof.
Instead, it adopts standard GC/OT security properties together with a
BitPriv-style publicly verifiable covert-security structure as the proof basis
for the implemented enforcement
model~\cite{BitPriv2025,Bellare2012FoundationsGC,LindellPinkas2008,Zhu2019PV2PC}.
Failures that would require violating Assumptions A1--A5 are outside the claim
scope.

\textbf{R1 (Input privacy).}
Input privacy inherits from the GC/OT construction.
In the auction computation used here, each buyer receives only the selected labels for
its own bid-wire range through OT and cannot infer other buyers' bids from this
local view. The garbler observes commitments and OT-level transcript
information, but does not learn buyers' private bid bits beyond output-implied
leakage.
Other buyers' selected labels are learned only at the label-availability step
required for selected-circuit evaluation. In the cooperative path this exchange
is off-chain; any on-chain fallback reveal is an explicit enforcement
disclosure and therefore part of the stated leakage boundary.
Therefore, under standard GC privacy and OT security assumptions (A1), seller
and buyer inputs remain hidden except for prescribed output leakage and explicit
enforcement disclosures.

\textbf{R2 (Output correctness and binding).}
GC correctness implies that honestly generated and evaluated circuits return
the global auction function
$F(\mathrm{reservePrice},\mathrm{bid}_1,\dots,\mathrm{bid}_n)$, encoded as:
\[
\begin{array}{l}
outputBytes = F(reservePrice, bid_1, \ldots, bid_n), \\
outputBytes = \texttt{encodePacked}(\texttt{winnerId}, \texttt{winningBid}, \texttt{chosenNamehash}).
\end{array}
\]
In the implementation, settlement is anchor-bound to the selected instance
$m$: the contract accepts only \texttt{outputBytes} consistent with committed
$\mathrm{hOut}_m$ and output-domain validity checks.
If a party submits \texttt{outputBytes} inconsistent with the committed anchor,
settlement is rejected; if opened-instance data are inconsistent, deterministic
seed-based reconstruction (A2) and dispute predicates expose the inconsistency.
Hence, under GC correctness, commitment binding, hash collision resistance, and
correct EVM execution (A1, A5), accepted settlement corresponds to an
anchor-bound output of the selected auction computation.

\textbf{R3 (Publicly verifiable accountability).}
Accountability follows from deterministic reconstruction plus publicly
checkable predicates for covered deviations.
For opened instances, challengers provide seed-derived artifacts, gate-leaf
evidence, and inclusion/transcript-root proofs; the contract recomputes the
relevant predicate and assigns blame deterministically.
If a dishonest deviation covered by the implemented predicates were not
attributable, then either commitment/hash binding fails, deterministic
reconstruction fails, or contract execution is incorrect---all excluded by
Assumptions A1--A5.
This yields selective public accountability for deviations covered by the
implemented dispute hooks.
Taken together, these sketches justify that the implemented protocol inherits
standard 2PC security properties while adapting enforcement to Ethereum
constraints.

\section{Economic-Security Requirements}
Security claim (2PC core): deviations that can be evidenced through verifiable
transcript checks should be economically dominated by honest execution.
Engineering choice (instantiation): this dominance is enforced through
deposits, slashing, and deadline rules in the contract layer. Beyond
cryptographic correctness, the thesis therefore requires \emph{economic
deterrence}: honest behavior should dominate profitable deviation in
expectation~\cite{BitPriv2025,Zhu2019PV2PC}.
This incentive-centric framing is aligned with mechanism-design analyses of Ethereum fee markets, where protocol rules directly shape strategic behavior and equilibrium outcomes~\cite{Roughgarden2021EIP1559}.
For a deviation strategy $\delta$, define
\[
U_{\delta}=G_{\delta}-p_{\mathrm{det}}\cdot L_{\delta}-C_{\delta},
\]
where $G_{\delta}$ is the potential gain from deviation,
$p_{\mathrm{det}}$ is the probability of successful detection/challenge,
$L_{\delta}$ is the financial loss under penalties/slashing if detected, and
$C_{\delta}$ is the operational cost of executing the deviation.
For garbler-side cheating analysis, $p_{\mathrm{det},G}$ denotes detection
probability induced by dispute predicates and enforcement checks (for example,
GC-leaf/OT-root disputes and timeout-triggered accountability).

The requirement is to parameterize deposits, slashing splits, and deadlines so
that, for relevant deviation classes,
\[
U_{\delta}\leq U_{\mathrm{honest}},
\]
and preferably $U_{\delta}<0$ for high-impact deviations.

For deterrence-oriented calibration, two practical inequalities are useful:
\begin{enumerate}
\item \textbf{Garbler-side cheating deterrence:}
\[
p_{\mathrm{det},G}\cdot D_G + C_G > G_G,
\]
equivalently
\[
D_G > \frac{G_G-C_G}{p_{\mathrm{det},G}} \quad (p_{\mathrm{det},G}>0),
\]
where $D_G$ is slashable garbler collateral, $G_G$ is expected gain from a
covered cheating strategy (for example, manipulating one gate/root/output), and
$C_G$ is attacker-side operational cost.
\item \textbf{Evaluator-side withholding/false-dispute deterrence:}
\[
\max\!\Big(
P_{\mathrm{false},j}+C_{\mathrm{disp},j},\;
P_{\mathrm{noreveal},j}+C_{\mathrm{withhold},j}
\Big)>B_{\mathrm{block},j},
\]
where $P_{\mathrm{false},j}$ is the penalty for an unsuccessful/false dispute by evaluator $E_j$,
$P_{\mathrm{noreveal},j}$ is the penalty for withholding required reveal/output progress near deadlines,
$C_{\mathrm{disp},j}$ is evaluator dispute transaction cost,
$C_{\mathrm{withhold},j}$ is the evaluator-side operational/transaction cost of a withholding strategy, and
$B_{\mathrm{block},j}$ is the expected benefit from delaying or preventing enforceable completion.
\end{enumerate}

These inequalities define the calibration method: deposit and penalty
parameters are chosen to satisfy the constraints under measured implementation
conditions.
For cut-and-choose strategies, $p_{\mathrm{det},G}$ is directly tied to opening
coverage: with one evaluation instance and the remaining instances opened, the
detection probability for inconsistencies on opened instances grows with $N$.
In the implemented PoC, $N=10$ is used as a conservative baseline that raises
opening coverage and supports practical deterrence in the evaluated scenarios.

Practically, this yields four design requirements:
\begin{enumerate}
\item \textbf{False-dispute deterrence:} unsuccessful challengers must incur loss.
\item \textbf{Invalid-opening deterrence:} inconsistent openings must be slashable with sufficient penalty.
\item \textbf{Abort deterrence:} withholding near deadlines should be financially dominated by honest completion.
\item \textbf{Cost-limited griefing:} the cost to delay others should be non-negligible for the attacker and limited for honest parties.
\end{enumerate}

Quantitative calibration depends on implementation-level observables (gas
profiles, artifact sizes, and latency/availability conditions). In this chapter,
we fix the calibration method and admissible constraints; numeric values used in
the experimental study are calibration baselines rather than normative protocol
constants. For the experimental baseline, we use a concrete parameter set (for example,
$N=10$, $n=3$, collateral $=1.2$ ETH, and explicit dispute deadlines encoded in
the contract) to demonstrate feasibility under deterministic conditions. These
values are chosen conservatively to cover worst-case transaction and data
availability behavior within the dispute window.

\section{Scope Boundaries for This Thesis}
This chapter formalizes the baseline target used throughout the remainder of
the thesis:
\begin{enumerate}
\item an economically secure 2PC enforcement model instantiated for a seller-to-many-buyers sealed-bid auction,
\item Ethereum L1 as the enforcement layer with contract-managed commitments, label availability, disputes, deadlines, and settlement transitions,
\item and constrained on-chain verification as the deployable enforcement model.
\end{enumerate}

In this instantiation, the auction computation is represented by one global
garbled auction circuit with seller-side and buyer-specific input-wire ranges.
The seller provides auction parameters, including the reserve price, each buyer provides
a private bid through OT-selected labels, and the selected computation produces
settlement output directly.

This work does not implement a general-purpose $n$-party MPC protocol. The
multi-buyer structure is specific to the auction circuit and its
contract-enforced label-availability, dispute, and settlement flow. General
$n$-party MPC, production-scale market design, and full game-theoretic
equilibrium proofs remain future work.

\chapter{Protocol Design}
\section{Design Objectives and Strategy}
The protocol is designed around three constraints that must hold at the same time:
\begin{enumerate}
\item private inputs are processed off-chain via garbled-circuit execution,
\item outcome enforcement remains publicly verifiable on Ethereum,
\item and deviations are deterred through deposits, slashing, and deadline-triggered fallback paths.
\end{enumerate}

This chapter specifies the protocol as designed and implemented in this thesis.
It presents an Ethereum-oriented state machine with
implementation-constrained checks, keeps expensive cryptographic work
off-chain, and reserves on-chain logic for commitment binding, selective
dispute predicates, and deterministic payout/assignment transitions.

\section{Protocol Artifacts and State}
For each cut-and-choose instance $i\in\{0,\dots,N-1\}$, the garbler commits to
the tuple:
\[
(\mathrm{comSeed}_i,\mathrm{rootGC}_i,\mathrm{blobHashGC}_i,\mathrm{hOut}_i).
\]
Each field has a specific role:
\begin{enumerate}
\item \textbf{$\mathrm{comSeed}_i$}: binding hash of the garbling seed for instance $i$.
\item \textbf{$\mathrm{rootGC}_i$}: terminal incremental-hash state over garbled-circuit artifacts used by the GC dispute predicate.
\item \textbf{$\mathrm{blobHashGC}_i$}: EIP-4844 blob hash commitment for evaluation payload publication in the evaluation instance~\cite{Buterin2022EIP4844}.
\item \textbf{$\mathrm{hOut}_i$}: output anchor
\[
\mathrm{hOut}_i = H(\texttt{"OUT"},\mathrm{circuitId},i,\mathrm{outputBytes}).
\]
\end{enumerate}

For each buyer $B_j$ and instance $i$, the garbler additionally commits
buyer-scoped OT transcript roots:
\[
\mathrm{rootOT}_{j,i}.
\]
These roots become challengeable on opened instances through deterministic
recomputation from revealed seed material (implementation excerpts:
Appendix~\ref{app:c1}--\ref{app:c2}).

For each buyer $B_j$, the protocol also models a commitment to the selected
input labels obtained through OT for the evaluation instance $m$:
\[
\mathrm{cLabel}_j = H(\texttt{"INLABEL"},\mathrm{circuitId},m,B_j,\mathrm{inputLabels}^m_j).
\]
where $\mathrm{inputLabels}^m_j$ denotes the selected input labels received by
buyer $B_j$ for its own bid wires in instance $m$.
This commitment binds the buyer to labels later shared off-chain or revealed
through the on-chain fallback path before settlement, without revealing the bid.

The verifier-side seed is produced from buyer commit-reveal inputs. Let
$s_j$ be the revealed seed of buyer $B_j$ (or $0$ when defaulted by liveness
logic). The protocol derives
\[
\mathrm{verifierSeed}=\bigoplus_j s_j,
\]
and selects the evaluation instance deterministically as
\[
m = H(\texttt{"M"},\mathrm{verifierSeed},\mathrm{circuitId},\mathrm{contractAddress}) \bmod N.
\]
This selection is intended to be unbiased with respect to the garbler. The
garbler does not control $\mathrm{verifierSeed}$, which is derived from
buyer commit-reveal inputs only. Because buyers commit
$H(\mathrm{seed},\mathrm{salt})$ before reveal, they cannot change committed
seeds after observing others. A late revealer may still try to withhold reveal
after seeing other reveals; this path is handled by deterministic
default-to-zero resolution and slashing. In addition, $\mathrm{circuitId}$ and
$\mathrm{contractAddress}$ are fixed before index finalization, and the
contract computes $m$ deterministically once the reveal/default-resolution
phase closes. Therefore, if at least one buyer contributes an unpredictable
seed, $m$ is pseudorandom from the garbler's perspective and cannot be biased
by garbler-side input selection. Attempted rerun-level bias by aborting is
economically deterred (under the protocol's utility assumptions) by collateral
and deadline penalties defined in the economic-security requirements; this is
an incentive argument, not a cryptographic impossibility claim.
All non-selected instances form the opened set $S_{\mathrm{open}}$ used for
cut-and-choose verification.

\section{Phase-by-Phase Protocol Flow}
\subsection{Pre-Phase: Participant Set}
Before deposits start, the seller/garbler and all buyers $B_1,\dots,B_n$ are
registered. The buyer set and receiver addresses are frozen for the run. The
auction circuit is fixed with separate input wires for the seller and for each
buyer.

\subsection{Phase 1: Deposits}
The seller/garbler and all registered buyers lock collateral. If deposits are
not completed before the deadline, refund paths allow participants to recover
funds. Successful completion advances the protocol to verifier-seed handling.

\subsection{Phase 2: Buyer Seed Commit-Reveal and Evaluation Index}
Each buyer first commits to a hash of $(seed, salt)$ and later reveals
$(seed, salt)$ during the reveal window. The contract checks that each reveal
matches the previously submitted commitment. Missing commits or reveals are
resolved by the default-to-zero rule and penalized according to the protocol
rules.

After all buyers are resolved, the contract derives the verifier seed and
computes the selected evaluation instance $m$. The value $m$ selects one
instance out of the $N$ cut-and-choose instances. This makes the selected
instance reproducible from on-chain state and prevents a party from choosing it
adaptively after seeing later commitments or evaluation payloads.

The selected index $m$ is then used in later phases: the garbler commits to
$blobHashGC_i$ and $hOut_i$ for all instances, and Phase~7 checks the
evaluation payload against the committed $blobHashGC_m$.

\subsection{Phase 3: Garbler Commitments}
The garbler submits the commitments needed for all $N$ circuit instances:
\begin{enumerate}
\item core commitments $(comSeed_i, rootGC_i, blobHashGC_i, hOut_i)$ for each
instance $i$;
\item buyer-scoped OT commitments $rootOT_{j,i}$ for each buyer $B_j$ and each
instance $i$.
\end{enumerate}

The output anchor $hOut_i$ binds the output bytes for instance $i$. The
buyer-scoped OT roots are needed because each buyer receives input labels for
its own bid wires through OT. If the garbler misses the deadline, buyers can
trigger the corresponding abort and penalty paths.

\subsection{Phase 4: Buyer OT Completion and Input-Label Commitments}
Each buyer $B_j$ completes OT for its own bid input wires and obtains the
selected input labels corresponding to its private bid. The buyer then commits
to these labels for the selected instance $m$:
\[
cLabel_j = H(\texttt{"INLABEL"}, circuitId, m, B_j, inputLabels^m_j),
\]
where $inputLabels^m_j$ are the selected input labels received by buyer $B_j$
for its own bid wires in instance $m$.

The bid itself is not revealed in this phase. The commitment only binds the
buyer to the labels it received through OT, so that later label sharing or
fallback reveal can be checked. If a buyer does not complete this phase before
the deadline, it is treated as non-cooperative, defaulted according to the
protocol rules, and penalized.

\subsection{Phase 5: Cut-and-Choose Openings}
The garbler reveals the seeds for all non-selected instances in $S_{open}$ and
proves consistency with the corresponding $comSeed_i$ commitments. Failure to
open consistently or on time leads to buyer-triggerable penalty paths.

Opened instances are used to check circuit consistency and buyer-scoped OT-root
consistency before settlement of the selected instance.

\subsection{Phase 6: Dispute Window}
During the dispute window, active buyers may challenge opened-instance data
through two dispute tracks:
\begin{enumerate}
\item \textbf{GC leaf dispute:} a buyer challenges one gate leaf on an opened
instance using the revealed instance seed, claimed gate leaf bytes,
incremental-hash proof to $rootGC_i$, and layout proof.

\item \textbf{Buyer-scoped OT root dispute:} for buyer $B_j$ and opened
instance $i$, the expected $rootOT_{j,i}$ is recomputed from the revealed seed
material and buyer-specific identifiers. A mismatch slashes the garbler; a
false challenge slashes the buyer.
\end{enumerate}

The protocol advances from the dispute window to seller-label reveal when all
active buyers close their dispute state or when the dispute deadline expires.

\subsection{Phase 7: Seller Label Reveal and Evaluation Payload Binding}
The seller/garbler reveals the seller-side input labels for the selected
instance $m$. In the same transition, the contract checks that the transaction
blob matches the committed $blobHashGC_m$. This binds settlement to the
evaluation payload committed for the selected instance.

This phase does not reveal buyer bids. Buyer labels remain the labels obtained
through OT and committed in Phase~4. The contract enforces payload binding and
phase correctness, while the full evaluation remains off-chain.

\subsection{Phase 8: Buyer Input-Label Availability}
Before settlement, the selected auction circuit can be evaluated only after the
seller-side labels from Phase~7 and the selected input labels of all active
buyers are available.

In the cooperative path, buyers share their committed input labels off-chain.
If a buyer withholds its labels, the fallback path requires that buyer to
reveal labels matching its Phase~4 commitment $cLabel_j$ on-chain, or be
penalized according to the liveness rules.

Once the required labels are available, any active buyer can evaluate the
selected auction computation and produce $outputBytes$.

If a buyer was defaulted, its bid input is fixed to the public default value
$0$. The labels for this default input are then used for that buyer's input
wires, so the circuit can still be evaluated without removing the buyer's input
range.

\subsection{Phase 9: Settlement and Assignment}
Any active buyer, or another authorized participant, can submit $outputBytes$
after the selected auction computation has been evaluated. The contract accepts
the submission only if:
\begin{enumerate}
\item $H(\texttt{"OUT"}, circuitId, m, outputBytes) = hOut_m$;
\item the decoded fields are well-formed and within bounds: winner id, winning
bid, and offered name hash.
\end{enumerate}

In this design, $outputBytes$ is the direct output of the selected auction
computation:
\[
outputBytes = \texttt{encodePacked}(\texttt{winnerId}, \texttt{winningBid}, \texttt{chosenNamehash}).
\]

After acceptance, the contract applies first-price payment logic, records the
winner metadata, and transitions to final ENS assignment and payout settlement.

\section{Multi-Buyer Auction Instantiation}
The auction instantiation coordinates one seller/garbler and $n$ buyers under a
single contract state machine. The auction computation is represented by one
global garbled circuit with seller-side and buyer-specific input-wire ranges.
Each buyer obtains only its own selected bid labels through OT and commits to
those labels. Before settlement, the required selected labels are made
available so that any active buyer can evaluate the selected auction
computation and derive \texttt{outputBytes}.

The multi-buyer orchestration relies on:
\begin{enumerate}
\item buyer-scoped OT transcript roots $\mathrm{rootOT}_{j,i}$,
\item buyer input-label commitments $\mathrm{cLabel}_j$,
\item per-buyer liveness/default handling,
\item per-buyer dispute closure tracking,
\item deterministic $m$ from aggregated buyer seed material,
\item one shared settlement output $\mathrm{hOut}_m$ for the selected auction computation.
\end{enumerate}
This keeps the enforcement logic participant-scoped while the auction result is derived
from one shared selected computation.

\section{Protocol vs Application Layer}
The protocol core is intentionally application-agnostic: commitments, openings,
disputes, deadlines, and settlement anchors are independent of specific
business rules. The ENS auction logic is the current application mapping:
\begin{enumerate}
\item the selected auction computation produces output bytes encoding winner identity, winning bid, and chosen name hash;
\item final assignment binds the chosen ENS name hash to the winner's registered receiver,
\item and first-price payment is executed from vault balances.
\end{enumerate}
The application layer validates and applies the settlement payload produced by
the selected auction computation.

The implementation currently models a fixed shortlist of offered ENS name hashes
and validates that the chosen output name belongs to that offered set. This is
an engineering simplification of the broader application vision and does not
change the protocol-level enforcement structure.

\section{Protocol-to-Implementation Alignment}
For reproducibility, the protocol notation and ordering in this chapter follow
the implemented state machine.
Output validity is specified via the structured anchor
$\mathrm{hOut}$ over packed output bytes, and the phase order places
verifier-seed finalization before the garbler's core commitment submission.
These choices keep the specification directly consistent with the contract-level
transition logic used in the prototype.

\chapter{Implementation (Proof of Concept)}
\section{System Architecture}
The proof-of-concept implements off-chain 2PC with on-chain enforcement.
The garbler and evaluators (buyers in the ENS-auction instantiation) run
cryptographic computation and evidence preparation off-chain, while Ethereum L1
enforces deadlines, commitments, disputes, and settlement transitions.
In the auction instantiation, these services jointly support the selected
auction computation: the garbler prepares the circuit instances, each buyer
obtains labels for its own input-wire range via OT, and settlement is derived
from the resulting \texttt{outputBytes}.

\begin{figure}[htbp]
\centering
\resizebox{0.94\textwidth}{!}{%
\begin{tikzpicture}[
  node distance=16mm and 18mm,
  box/.style={draw, rounded corners=2pt, align=center, minimum width=40mm, minimum height=10mm},
  >={Latex[length=2.5mm]}
]
  \node[box, fill=green!15, xshift=4mm] (alice) {\textbf{Garbler Off-Chain Service}\\garbling, commitments, openings, proofs};
  \node[box, fill=green!15, below=of alice] (bobs) {\textbf{Evaluator Off-Chain Services}\\$E_1, E_2, \dots, E_n$ evaluation and challenges};
  \node[box, fill=yellow!20, right=40mm of alice, yshift=-8mm, minimum width=52mm, minimum height=16mm] (contract) {\textbf{Ethereum L1 Contract}\\state machine, deadlines,\\deposits, disputes, settlement};

  \draw[<->, thick] (alice) -- node[left, align=center] {off-chain protocol exchange\\(seeds, artefacts, proofs)} (bobs);
  \draw[->, thick] (alice) -- node[above, align=center] {on-chain actions\\(commit/reveal/dispute)} (contract);
  \draw[->, thick] (bobs.east) -- node[pos=0.78, below, yshift=-3.5mm, align=center, text width=33mm] {on-chain actions\\(ready/challenge/settle/abort)} (contract.west);
\end{tikzpicture}
}
\caption{Prototype protocol architecture with one garbler role, $n$ evaluator roles, and Ethereum L1 contract enforcement.}
\label{fig:prototype-architecture}
\end{figure}

\section{On-Chain Architecture}
\subsection{State Machine and Core Objects}
At contract level, the enforcement contract models the protocol as an explicit
finite state machine with hard deadlines.
The stages include deposits, buyer seed commit/reveal, core commitments,
buyer-scoped OT commitments, buyer OT completion, input-label commitment,
and liveness/default handling, opening,
dispute, label reveal, settlement, assignment, and closure.

Protocol-critical commitment objects are stored per cut-and-choose instance:
\[
(\mathrm{comSeed}_i,\mathrm{rootGC}_i,\mathrm{blobHashGC}_i,\mathrm{hOut}_i),
\]
and per buyer-instance OT commitments:
\[
\mathrm{rootOT}_{j,i}.
\]
This state layout directly supports dispute traceability and deterministic verification for opened instances.

\subsection{Phase Handlers}
The contract exposes dedicated handlers for each transition class:
\begin{enumerate}
\item \textbf{Seed handling and evaluation index derivation:} buyer seed commit and reveal finalization, plus deterministic $m$ selection.
\item \textbf{Commitment publication:} the garbler submits core commitments, then OT roots per buyer.
\item \textbf{Buyer input-label handling:} buyers complete OT for their own input-wire ranges, commit to selected labels, and unresolved buyers are defaulted/slashed after deadline to preserve protocol progress.
\item \textbf{Opening and dispute entry:} the garbler reveals $N-1$ openings; active buyers enter dispute window.
\item \textbf{Buyer label availability before settlement:} committed selected labels are made available through cooperative off-chain exchange or on-chain fallback disclosure in the protocol design.
\item \textbf{Settlement and assignment:} output anchor validation, vault updates, winner recording, and final assignment.
\end{enumerate}

This implementation structure keeps transition logic auditable on-chain and cross-phase behavior unambiguous.

\subsection{Dispute and Accountability Mechanism}
Two explicit dispute predicates are implemented on-chain:
\begin{enumerate}
\item \textbf{GC leaf dispute:} verifies one challenged gate leaf on an opened instance via seed-consistent recomputation, incremental-hash proof, and layout proof.
\item \textbf{Buyer-scoped OT root dispute:} recomputes expected OT root for one buyer/evaluator and one opened instance; mismatch slashes garbler, false challenge slashes the challenger.
\end{enumerate}

The dispute window closes either when all active buyers close their dispute
state or when deadline-based finalization is triggered.
The design provides constrained on-chain verification while preserving economically enforceable blame assignment.

\subsection{Settlement and Assignment Path}
Settlement accepts an output only if the computed anchor equals committed $\mathrm{hOut}_m$ for the evaluation instance.
It then decodes the accepted output into winner id, winning bid, and chosen name hash.
Next, the contract applies first-price vault transfer logic and executes assignment in a separate finalization step.
This separation keeps settlement correctness checks explicit and makes payout/assignment transitions observable on-chain.
The submitted \texttt{outputBytes} are treated as the encoded output of the
selected auction computation. The contract does not recompute the auction
function on-chain; it checks $\mathrm{hOut}$ binding and domain validity before
applying settlement.

\subsection{Core Security Snippets}
The four core aspects below are kept in the main implementation chapter as
compact anchors; extended code context is provided in the appendices.

\begin{lstlisting}[style=soliditysnippet,caption={Stage/role gating and timeout-enforced liveness in seed commit phase.},label={lst:seed-commit-liveness}]
function commitBuyerSeed(bytes32 commitment) public {
    require(currentStage == Stage.BuyerSeedCommit, "Wrong stage");
    require(block.timestamp <= deadlines.verifierSeed, "Seed-commit deadline missed");
    require(isBuyer[msg.sender], "Only buyer");
    require(commitment != bytes32(0), "Empty buyer seed commitment");
    require(buyerSeedCommitment[msg.sender] == bytes32(0), "Buyer seed already committed");
    buyerSeedCommitment[msg.sender] = commitment;
}

function finalizeBuyerSeedCommitAfterDeadline() public {
    require(currentStage == Stage.BuyerSeedCommit, "Wrong stage");
    require(block.timestamp > deadlines.verifierSeed, "Seed-commit phase still active");
    require(_isParticipant(msg.sender), "Only participant");
    // Non-committed buyers are defaulted to seed=0 and slashed.
}
\end{lstlisting}

\begin{lstlisting}[style=soliditysnippet,caption={Blob-hash commitment check before label reveal for instance $m$.},label={lst:blob-binding}]
function revealGarblerLabels(bytes32[] calldata _labels) external {
    require(currentStage == Stage.Labels, "Wrong stage");
    require(msg.sender == alice, "Only Garbler");
    require(block.timestamp <= deadlines.labels, "Label reveal deadline missed");
    require(_labels.length == bitWidth, "Bad labels length");

    bytes32 bHash = blobhash(0);
    require(bHash != bytes32(0), "Garbled Table Blob missing");
    require(bHash == instanceCommitments[m].blobHashGC, "Blob does not match committed evaluation blob hash");

    garblerLabels = _labels;
}
\end{lstlisting}

\begin{lstlisting}[style=soliditysnippet,caption={Bounded GC-leaf dispute check with slashing outcome.},label={lst:gc-dispute}]
function challengeGateLeaf(
    uint256 instanceId,
    uint256 gateIndex,
    GateDesc calldata g,
    bytes calldata leafBytes,
    bytes32[] calldata ihProof,
    bytes32[] calldata layoutProof
) public {
    require(currentStage == Stage.Dispute, "Wrong stage");
    require(block.timestamp <= deadlines.dispute, "Dispute deadline missed");
    require(isBuyer[msg.sender], "Only buyer for dispute");
    require(buyerStatus[msg.sender] == BuyerStatus.Ready, "Buyer not active in dispute");

    _assertValidLayoutProof(gateIndex, g, layoutProof);
    bytes32 seed = _requireRevealedSeedForOpenedInstance(instanceId);
    bytes32 leafHash = _gateLeafHash(gateIndex, leafBytes);
    require(_processIncrementalProof(leafHash, ihProof) == instanceCommitments[instanceId].rootGC, "Bad IH proof");

    bytes memory expected = recomputeGateLeafBytes(seed, instanceId, gateIndex, g);
    bool matchLeaf = (_gateLeafHash(gateIndex, expected) == leafHash);
    if (!matchLeaf) _slashAliceToAllBuyers();
    else _slashBuyerToAlice(msg.sender);
}
\end{lstlisting}

\begin{lstlisting}[style=soliditysnippet,caption={Settlement anchor binding and output-domain checks.},label={lst:settlement-binding}]
function settle(bytes calldata outputBytes) external {
    require(currentStage == Stage.Settle, "Wrong stage");
    require(_isParticipant(msg.sender), "Only participant");
    require(block.timestamp <= deadlines.settle, "Settlement deadline missed");
    require(_computeOutputAnchor(m, outputBytes) == instanceCommitments[m].hOut, "Invalid output commitment");

    (uint16 outWinnerId, uint64 outWinningBid, bytes32 outChosenNamehash) = _decodeOutput(outputBytes);
    require(outWinnerId < buyers.length, "winnerId out of bounds");
    require(uint256(outWinningBid) <= vault[buyers[outWinnerId]], "winningBid exceeds winner vault");
    require(
        outChosenNamehash == offeredNamehashes[0] ||
        outChosenNamehash == offeredNamehashes[1] ||
        outChosenNamehash == offeredNamehashes[2],
        "chosenNamehash not offered"
    );
}
\end{lstlisting}

\subsection{Code Excerpt Roadmap}
Excerpts illustrate enforcement, while the security argument is in Chapter~3/4.
To keep the main narrative focused, full code excerpts are grouped in appendices
and referenced from the mechanism discussion:
\begin{enumerate}
\item state machine, deadlines, and timeout progression:
Appendix~\ref{app:a1},
\item settlement anchor binding and output decoding:
Appendix~\ref{app:a2},
\item dispute predicates and slashing resolution:
Appendix~\ref{app:a3}, Appendix~\ref{app:b2}, Appendix~\ref{app:b3},
Appendix~\ref{app:c1}, and Appendix~\ref{app:c2},
\item blob-hash data-binding reference:
Appendix~\ref{app:a4},
\item auction-output encoding and settlement-anchor path:
Appendix~\ref{app:d1},
\item end-to-end scenario mapping:
Appendix~\ref{app:d2}.
\end{enumerate}

\subsection{Application Layer: ENS Auction}
In this proof-of-concept, the protocol is instantiated as an ENS auction application.
The application-specific mapping is implemented as follows:
\begin{enumerate}
\item bids are provided by buyers $B_1,\dots,B_n$ as private inputs to the auction computation, and the selected computation computes the winner outcome;
\item the settlement payload encodes winner ID, winning bid, and chosen name hash,
\item the contract checks that the chosen name hash is offered and that the winning bid is economically valid,
\item final assignment is executed by calling the ENS adapter with the winner receiver address after settlement finalization.
\end{enumerate}
In the prototype, this computation is implemented as a global garbled circuit.
The ENS layer does not compute the maximum bid itself; it consumes the
circuit-produced \texttt{outputBytes} and applies assignment/payment rules.
This makes the ENS auction an implemented application layer over the protocol core rather than only an abstract example.

\section{Off-Chain Architecture}
\subsection{Shared Protocol Library}
The crate \texttt{off-chain-common} defines shared deterministic protocol logic
used by both garbler and evaluator services:
\begin{enumerate}
\item global auction circuit layout and input-wire partitioning,
\item garbling/evaluation helpers,
\item incremental-hash and Merkle utilities for dispute evidence,
\item OT transcript reconstruction and root derivation,
\item buyer input-label commitment encoding,
\item auction-output encoding and $\mathrm{hOut}$ derivation,
\item canonical evaluation blob encoding and EIP-4844 versioned-hash derivation.
\end{enumerate}
Using one shared library is a protocol-integrity decision: both roles derive identical hashes, roots, and anchors from the same inputs.

\subsection{Garbler Off-Chain Service}
The \texttt{off-chain-alice} service performs garbler-side preparation and publication.
Its command set covers deposit, commitment construction, OT-root submission,
opening reveal, label reveal, and evaluation artifact export.
Garbler-side tooling produces the exact commitment tuple expected by the
contract and can emit evaluation payload artifacts for blob-linked settlement
flow.

\subsection{Evaluator Off-Chain Services}
The \texttt{off-chain-bob} service performs evaluator-side actions for each
evaluator $E_j$ (buyer $B_j$ in the ENS application):
\begin{enumerate}
\item seed commit/reveal and liveness signaling,
\item OT completion for the evaluator's own input-wire range,
\item selected input-label commitment after OT,
\item cooperative exchange or fallback preparation for committed input labels before settlement,
\item evaluation of the selected auction computation once seller labels and all required buyer labels are available,
\item dispute packet preparation (GC leaf track and OT-root track),
\item settlement submission and assignment finalization.
\end{enumerate}
This role separation supports the multi-buyer auction instantiation while preserving one
shared protocol logic core.

\section{Protocol-to-Code Mapping}
Implementation traceability is one of the core PoC goals.
Accordingly, the protocol phases in Chapter~4 map to concrete implementation entry points as follows:
\begin{enumerate}
\item \textbf{Deposits and buyer registration/readiness:} contract deposit and participant-activation paths plus buyer-side readiness commands.
\item \textbf{Verifier-seed commit/reveal:} buyer commit/reveal handlers on-chain and corresponding buyer commands off-chain.
\item \textbf{Core commitments and OT roots:} garbler commitment and OT-root submission handlers on-chain, commitment builders in garbler service.
\item \textbf{Buyer OT and input-label commitments:} buyer OT completion and selected-label commitment handling.
\item \textbf{Opening and dispute:} reveal-openings, dispute handlers, and off-chain dispute packet generation.
\item \textbf{Buyer input-label availability:} cooperative off-chain label exchange or on-chain fallback preparation before settlement.
\item \textbf{Settlement and assignment:} selected auction-computation \texttt{outputBytes} derivation, $\mathrm{hOut}$ anchor derivation, then on-chain settlement and assignment handlers.
\end{enumerate}

The key point is that the main enforcement mechanisms are not narrative-only: deposits, seed handling, commitments, openings, disputes, settlement-anchor checks, and assignment are reflected in executable Solidity and Rust code paths.

\section{Implementation Design Choices and Scope}
This thesis uses a proof-of-concept implementation to validate end-to-end
protocol enforceability.
Three choices are deliberate protocol-engineering decisions:
\begin{enumerate}
\item \textbf{Shared deterministic GC/OT rules across Solidity and Rust:} the constrained canonical representation is required to guarantee verifier parity.
\item \textbf{Constrained on-chain verification:} leaf-level and root-level checks are chosen to keep verification gas-limited and deployable on Ethereum.
\item \textbf{Hash-bound evaluation payload publication:} blob-hash commitment checks enforce data binding for settlement while keeping heavy data handling off the contract path~\cite{Buterin2022EIP4844}.
\end{enumerate}

The implementation therefore serves as an end-to-end feasibility validation of
the protocol model under Ethereum constraints.
It validates the enforcement skeleton: commitments, roots, openings, disputes,
\(\mathrm{hOut}\)-bound settlement, and assignment.
The protocol description treats auction computation as a selected private
computation in the enforcement flow;
implementation-specific deterministic output-encoding helpers are presented as
evidence for settlement binding, not as a separate application-layer
aggregation rule.

\section{Validation and Reproducibility}
Validation is organized into three layers:
\begin{enumerate}
\item \textbf{Smart-contract tests:} the 2PC protocol test suite covers transition, timeout, dispute, settlement, and ENS-assignment behavior. Lifecycle behavior is covered in a dedicated lifecycle suite.
\item \textbf{Off-chain deterministic tests:} off-chain-common integration tests check parity and encoding. Coverage includes cut-and-choose and OT flows, settlement-anchor derivation, eval-blob checks, and EIP-4844 hash derivation.
\item \textbf{End-to-end scenario script:} dedicated demo coverage for honest success, evaluator default, and garbler-cheat dispute flows.
\end{enumerate}

Together, these three validation layers are the reproducibility baseline for the implemented protocol and its ENS auction application path.

\chapter{Evaluation}
\section{Evaluation Objectives}
This chapter evaluates protocol-core enforcement costs with the ENS auction as
the concrete application instantiation.
The goal is to provide implementation-backed evidence across four layers:
\begin{enumerate}
\item scenario validation under honest and adversarial flows,
\item on-chain enforcement cost profile (per-call gas and per-scenario totals),
\item off-chain/runtime and artifact-size measurements,
\item moderate scaling indicators over evaluator count \(n\) and cut-and-choose parameter \(N\).
\end{enumerate}

\section{Methodology and Experimental Setup}
\subsection{Measured Quantities}
The instrumentation records five measurement groups:
\begin{enumerate}
\item per-transaction gas usage for protocol-relevant calls,
\item per-scenario totals: gas, transaction count, terminal stage, and final settlement, assignment, and slashing outcomes,
\item off-chain wall-clock timings for selected CLI operations,
\item serialized artifact sizes and structural counts,
\item scaling indicator tables for \(n\)- and \(N\)-sensitivity.
\end{enumerate}

\subsection{Execution Environment}
Evaluation runs were executed on a local deterministic Anvil chain.
Two harnesses were used: an automated scenario harness
(honest/default/cheat) and a dedicated moderate scaling sweep harness
(\(n\)- and \(N\)-sensitivity points).

For the measured baseline, the protocol parameters were:
\begin{enumerate}
\item number of cut-and-choose instances: $N=10$,
\item number of evaluators (buyers in the ENS application): $n=3$,
\item circuit bit width: $57$ (chosen so the bid domain for this baseline stays below the 1.2 ETH collateral cap),
\item collateral per participant: $1.2$ ETH,
\item auction rule: first-price settlement with deterministic winner decoding.
\end{enumerate}

The role split between parameters is intentional:
\(N\) controls cut-and-choose verification coverage, while \(n\) sets the size
of the auction instantiation.

Local deterministic execution gives reproducible behavior and cost traces.
Production fee calibration still depends on deployment-specific gas-price and
blob-fee assumptions.

\subsection{Scenario Matrix}
\begin{table}[htbp]
\centering
\resizebox{\linewidth}{!}{%
\begin{tabular}{|p{2.8cm}|p{4.2cm}|p{7.4cm}|}
\hline
\textbf{Scenario} & \textbf{Injected condition} & \textbf{Expected property check} \\
\hline
Honest success flow & No deviations by garbler or evaluators & Protocol reaches Closed; settlement is accepted; ENS assignment completes; no unresolved evaluators remain. \\
\hline
Evaluator defaulted flow & One buyer/evaluator does not complete OT/input-label commitment before the buyer-input deadline & Default-to-zero and slashing are applied; protocol still reaches settlement, then assignment. \\
\hline
Garbler-cheat flow & Garbler commits tampered rootGC for an opened instance & GC-leaf dispute succeeds; garbler is slashed; contract closes without settlement or assignment. \\
\hline
\end{tabular}
}
\caption{End-to-end evaluation scenarios used for protocol validation.}
\label{tab:evaluation-scenarios}
\end{table}

\section{Scenario Results}
\input{evaluation/tables/scenario_summary.tex}

Across all executed runs, the following invariants were confirmed:
\begin{enumerate}
\item honest execution reached \texttt{Closed} with accepted settlement and completed assignment,
\item evaluator default triggered deterministic default/slashing while preserving liveness,
\item garbler cheating was attributed via GC-leaf dispute, with deterministic slashing and closure without settlement.
\end{enumerate}

\section{Requirement Coverage from the Results}
The executed scenarios provide direct evidence for key requirements from
Chapter~3:
\begin{enumerate}
\item \textbf{R2 (Output correctness and binding):} Scenario 1 and Scenario 2 accepted settlement only with valid \texttt{hOut}-bound output bytes and domain-constrained decoded fields.
\item \textbf{R3 (Publicly verifiable accountability):} Scenario 3 shows objective, contract-verifiable evidence leading to deterministic slashing of a cheating party.
\item \textbf{R4 (Liveness with penalties):} Scenario 2 demonstrates progress despite non-cooperative evaluator behavior via default and slashing.
\item \textbf{R5 (Settlement integrity):} successful scenarios complete deterministic first-price transfer and assignment in a protocol-consistent terminal state.
\end{enumerate}

\section{Cost and Performance Discussion}
\subsection{Per-call Gas Profile}
\input{evaluation/tables/gas_by_call.tex}
The per-call profile shows that commitment publication dominates the optimistic
path.
\texttt{submitCommitments} and buyer-scoped
\texttt{submitOtRootsForBuyer} are the largest recurring costs.
Opening and dispute-phase closure calls are moderate by comparison, while
\texttt{disputeGarbledTable} is the dominant selective-verification cost in the
cheating path.

\subsection{Total Scenario Cost}
\input{evaluation/tables/scenario_cost_totals.tex}
Scenario totals confirm the expected behavior-level trade-off.
The default scenario remains close to honest execution because the same main
phases execute, with timeout/default replacing one evaluator readiness path.
The cheating scenario skips settlement/assignment but includes a heavy dispute
transaction, yielding a comparable total range.

\subsection{Artifact Sizes}
\input{evaluation/tables/artifact_sizes.tex}
Artifact measurements reflect the intended design split.
Settlement-critical payloads such as \texttt{outputBytes} stay compact and
fixed-size, while the evaluation blob dominates raw bytes and remains off-chain
except for hash-bound enforcement hooks.
This is consistent with constrained on-chain verification and heavier data
handling outside contract state.

\subsection{Off-chain Runtime}
\input{evaluation/tables/runtime_observed.tex}
Observed local runtimes for the profiled CLI operations are in the millisecond
range and remain stable across the baseline scenarios.
Commitment preparation and label-reveal-related steps are the largest measured
off-chain contributors, while output encoding/anchor derivation is
comparatively small.
These values are implementation timings.
They are intended for reproducibility and relative comparison, not as
hardware-independent benchmarks.

\subsection{Scaling Indicators}
\input{evaluation/tables/scaling_buyers.tex}
\input{evaluation/tables/scaling_instances.tex}
The scaling tables show the expected trend behavior for the implemented model.
At fixed \(N=10\), total gas grows with \(n\) due to buyer-scoped publication
and closure tracking work.
At fixed \(n=3\), increasing \(N\) increases commitment/opening-related costs
through larger cut-and-choose evidence surfaces.
These measurements evaluate the enforcement state machine and settlement-binding
path of the PoC.
Within the protocol model used in this thesis, auction results are outputs of
the selected auction computation, so the reported \(n\)-sensitivity reflects
buyer-scoped commitments, OT roots, readiness/default handling, and dispute
closure tracking.

At fixed \(N=10\), increasing \(n\) primarily scales buyer-scoped OT roots
(\(O(nN)\)) and evaluator closure state (\(O(n)\)).
At fixed \(n=3\), increasing \(N\) scales core commitments (\(O(N)\)),
buyer-scoped OT roots (\(O(nN)\)), and opening payload size (\(O(N)\)).
The dedicated scaling sweep executes full honest-success runs for all planned
points (\(n \in \{1,3,5,10\}\), \(N=10\) and \(n=3\), \(N \in \{5,10,20\}\)),
and records measured totals for each point. These totals are reported as
trend indicators from deterministic local execution and are not presented as
production throughput limits.

Scenario totals and scaling totals are intentionally reported from two
measurement harnesses with different purposes.
The scenario harness replays protocol-generated artifacts for
honest/default/cheat behavior and reports scenario outcomes (deployment
excluded, buyer registration included).
The scaling harness re-deploys per point and runs only the honest-success path
with deterministic synthetic commitment vectors to normalize
\(n,N\)-sensitivity.
Therefore, shared coordinates (for example \(n=3, N=10\)) are interpreted
within harness context rather than as strict cross-harness equality checks:
scenario tables support behavioral validation, while sweep tables support
growth-trend validation.

Accordingly, the sweep supports structural cost analysis for the implemented
enforcement model, while deployment-calibrated economics remain future work.

\section{Qualitative Positioning}
\input{evaluation/tables/approach_comparison.tex}

The comparison is positioning-oriented: it highlights trust/cost trade-offs and
scope boundaries, not universal superiority claims.
For timing-sensitive blockchain baselines such as commit-reveal, this perspective is consistent with consensus models that explicitly account for partial participation over time~\cite{PassShi2017Sleepy}.
\clearpage

\section{Threats to Validity}
The evidence is strong for implementation-level protocol behavior, but external
validity remains bounded:
\begin{enumerate}
\item local execution does not model live mempool competition or adversarial
transaction ordering,
\item gas values here are execution-cost measurements, not final fee
predictions under volatile base-fee/blob-fee conditions,
\item the \(n,N\) sweep is moderate and trend-oriented; broad throughput limits
are out of scope,
\item off-chain timing values depend on local hardware and implementation
maturity,
\item debugging output in the experimental execution harness is not part of the
privacy-preserving protocol interface.
\end{enumerate}

\chapter{Discussion and Conclusion}
\section{Discussion of the Main Findings}
We set out to design and validate an economically secure 2PC protocol for
Ethereum, with sealed-bid auctions as the concrete application context. The
implementation and evaluation show that this objective is feasible when
enforcement is encoded as a strict on-chain state machine while heavy private
computation remains off-chain.

Three implemented findings are central.
First, \textbf{output binding and settlement integrity} are enforceable through
anchor checks (\texttt{hOut}) and deterministic output decoding constraints.
Second, \textbf{accountability under deviation} is achieved through scoped
dispute predicates (GC-leaf and evaluator-scoped OT-root tracks) with
deterministic slashing outcomes.
Third, \textbf{liveness under strategic behavior} is preserved through
deadline-driven default and penalty transitions.

Taken together, these findings indicate that privacy-preserving computation can
be embedded into practical Ethereum settlement workflows through commitments,
deadlines, and selective challenge predicates, without requiring universal
on-chain re-execution.

The implementation process also surfaced three design lessons. Deployability
constraints are first-order protocol parameters, cost-aware verification design
is necessary for L1 feasibility, and protocol simplicity materially improves
end-to-end implementability and auditability.

These conclusions remain consistent with publicly verifiable financially secure
2PC directions in prior work, while grounding them in a concrete,
deployment-oriented enforcement model for Ethereum~\cite{Zhu2019PV2PC,BitPriv2025}.

\section{Protocol-Core vs Application Layer}
A key architectural choice is the separation between a reusable protocol core
and application-specific market logic.
Commitment lifecycle, deadlines, dispute predicates, and settlement binding are
protocol-core mechanisms; the ENS auction is one application-layer
instantiation over that backbone, realized here by first-price settlement and
deterministic assignment of the selected namehash.

This separation improves architectural transferability while limiting
application-specific assumptions in the protocol-core security and enforcement
model.
The same core can be instantiated for sealed tenders, private matching,
confidential allocation, or selective procurement, provided outcomes can be
encoded into anchor-bound settlement bytes with deterministic execution rules.
It also enables auction-mechanism upgrades at the application layer without
redesigning the enforcement core.

\section{Limitations}
The contribution is established within explicit technical boundaries:
\begin{enumerate}
\item \textbf{Incentive model scope:} the protocol enforces deposits, deadlines,
and challenge costs, and demonstrates deterministic slash/default outcomes in
representative adversarial flows; it does not provide a full formal equilibrium
proof (e.g., Nash or subgame-perfect) over all strategic actor behaviors.
\item \textbf{Deployment economics scope:} gas values are measured under
deterministic local execution and support reproducible execution-cost
comparison; they are not direct production fee predictions under dynamic
base-fee, priority-fee, and blob-fee conditions.
\item \textbf{Verification scope:} the enforcement model is based on
bounded/selective dispute predicates and settlement-time binding checks, rather
than universal on-chain re-execution of the complete private computation.
\item \textbf{Multi-party scope:} the auction instantiation uses one global
garbled auction circuit with buyer-specific input-wire ranges and buyer-scoped
OT handling.
This is not a general-purpose \(n\)-party MPC protocol; it is a structured
seller-to-many-buyers auction circuit with contract-enforced commitments, label
availability, and settlement binding.
\item \textbf{Benchmark scope:} the evaluation validates scenario correctness and
moderate scaling trends in \(n\) and \(N\), but does not claim production
throughput ceilings or adversarial network-stress limits.
\item \textbf{Application-mechanism scope:} the ENS instantiation demonstrates
architectural transferability, but does not establish welfare-optimality or
incentive properties across broader private auction mechanisms.
\end{enumerate}

These boundaries clarify what is demonstrated and measured in this thesis, and
they define a precise extension surface for follow-on work.

\section{Future Work}
Near-term engineering work concerns deployment calibration and broader empirical
validation:
\begin{enumerate}
\item \textbf{Production fee calibration and deployment-level benchmarking:} map measured execution gas to deployment fee assumptions (base fee, priority fee, blob fee) and evaluate cost robustness across realistic network conditions~\cite{Buterin2022EIP4844}.
\item \textbf{Robustness and stress validation:} extend scenario campaigns to
larger evaluator sets and richer adversarial combinations, including
adversarial timing and execution ordering conditions.
\item \textbf{Tooling and automation:} strengthen reproducibility through tighter
measurement pipelines, scenario orchestration, and regression automation for
cost, dispute, and settlement invariants.
\item \textbf{Broader empirical scaling:} expand \(n,N\)-sweep coverage while
preserving deterministic harness semantics and comparable reporting criteria.
\end{enumerate}

Longer-term research directions concern formal strategic guarantees and protocol
generalization:
\begin{enumerate}
\item \textbf{Formal strategic analysis:} derive explicit equilibrium-level
conditions for collateral, deadlines, and challenge pricing under richer
attacker models.
\item \textbf{General-purpose multi-party variants:} evaluate protocol families
that support broader \(n\)-party private computation beyond the structured
global auction circuit used here.
\item \textbf{Richer private market mechanisms:} generalize beyond the current
first-price ENS mapping toward alternative allocation and pricing rules.
\item \textbf{Stronger privacy/composability models:} refine compositional
security arguments for combined off-chain computation, selective dispute
exposure, and repeated-market operation.
\item \textbf{Alternative settlement layers:} compare trust/performance tradeoffs
of additional blockchain settlement environments and cross-layer architectures
while preserving the enforcement-first contribution of this work~\cite{Haloani2024COTIv2}.
\end{enumerate}

\section{Conclusion}
The central result is that privacy-preserving market execution on Ethereum can
be achieved through economically enforceable off-chain computation, without
requiring full on-chain private computation.

Our implemented Solidity/Rust prototype demonstrates that commitments,
deadlines, selective disputes, and deterministic settlement can be composed
into a coherent L1 enforcement workflow under a concrete auction
instantiation.
This establishes a deployment-oriented design pattern for private market
mechanisms on public blockchains.

Overall, we provide a credible L1-native path toward enforceable private market
execution through disciplined protocol engineering and economic alignment.

\appendix

\chapter{On-Chain Enforcement Excerpts}
\label{app:onchain}
Excerpts illustrate enforcement; the security argument is in Chapter~3/4.
This appendix provides implementation evidence for the enforcement mechanisms.

\section{State Machine and Deadlines}
\label{app:a1}
\lstinputlisting[
  style=soliditysnippet,
  caption={Stage and deadline data structures.},
  firstline=31,
  lastline=69
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Representative transition with stage/deadline gating: deposit phase.},
  firstline=193,
  lastline=208
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Representative timeout/escape-hatch progression in dispute closure.},
  firstline=842,
  lastline=870
]{contract/src/MillionairesProblem.sol}

\section{Settlement Binding and Output Decoding}
\label{app:a2}
\lstinputlisting[
  style=soliditysnippet,
  caption={Output anchor hash and output tuple decoding helpers.},
  firstline=658,
  lastline=677
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Settlement checks: hOut binding, tuple bounds, and offered-name validation.},
  firstline=685,
  lastline=708
]{contract/src/MillionairesProblem.sol}

\section{Dispute and Slashing Logic}
\label{app:a3}
\lstinputlisting[
  style=soliditysnippet,
  caption={GC-leaf dispute path with deterministic slashing branch.},
  firstline=1071,
  lastline=1102
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Economic-resolution payout handlers used by dispute outcomes.},
  firstline=804,
  lastline=840
]{contract/src/MillionairesProblem.sol}

\section{Blob Binding Reference (EIP-4844)}
\label{app:a4}
\lstinputlisting[
  style=soliditysnippet,
  caption={Blob-hash commitment check before entering settlement.},
  firstline=599,
  lastline=613
]{contract/src/MillionairesProblem.sol}
This check is the concrete code hook for the dispute-window availability
assumption in Chapter~3 (Assumption A4).

\chapter{Garbled-Circuit Mechanics Excerpts}
\label{app:gc}
\section{Wire Label Derivation and Point-and-Permute}
\label{app:b1}
\lstinputlisting[
  style=soliditysnippet,
  caption={Wire flip bit and deterministic label derivation with permutation-bit embedding.},
  firstline=878,
  lastline=912
]{contract/src/MillionairesProblem.sol}

\section{Gate Leaf Recompute and Encoding Layout}
\label{app:b2}
\lstinputlisting[
  style=soliditysnippet,
  caption={Per-gate leaf recomputation for AND/XOR/NOT and canonical packed leaf bytes.},
  firstline=941,
  lastline=1005
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Canonical leaf byte length constant used by dispute validation.},
  firstline=1010,
  lastline=1019
]{contract/src/MillionairesProblem.sol}

\section{Incremental-Hash and Layout-Merkle Verification}
\label{app:b3}
\lstinputlisting[
  style=soliditysnippet,
  caption={Layout membership check against committed circuit layout root.},
  firstline=1035,
  lastline=1044
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Incremental-hash proof processing for index-bound GC leaf inclusion.},
  firstline=1140,
  lastline=1154
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Layout leaf hash construction used by the layout Merkle proof.},
  firstline=1132,
  lastline=1134
]{contract/src/MillionairesProblem.sol}

\chapter{OT Transcript Commitment and Recompute}
\label{app:ot}
\section{OT Transcript Leaf Hashing and Root Tree}
\label{app:c1}
\lstinputlisting[
  style=soliditysnippet,
  caption={Transcript leaf hashing and commutative node hashing primitives.},
  firstline=1155,
  lastline=1172
]{contract/src/MillionairesProblem.sol}

\lstinputlisting[
  style=soliditysnippet,
  caption={Deterministic OT-root recomputation from transcript components.},
  firstline=1249,
  lastline=1292
]{contract/src/MillionairesProblem.sol}

\section{OT Payload Hash Derivation}
\label{app:c2}
In the global auction-circuit model, buyer input wires are buyer-scoped. The
excerpt below uses a simplified helper name
\texttt{\_evaluatorWireId(inputBit)}, but the intended mapping is buyer-specific
and domain-separated by buyer address, e.g.,
\texttt{\_buyerWireId(buyerAddr, inputBit)}.
\lstinputlisting[
  style=soliditysnippet,
  caption={Per-round OT payload hash derivation bound to buyer, instance, wire id, and seeds.},
  firstline=1179,
  lastline=1247
]{contract/src/MillionairesProblem.sol}

\chapter{Off-Chain Orchestration Evidence}
\label{app:orchestration}
\section{Global-Circuit Output Encoding and Settlement Anchor}
\label{app:d1}
The auction maximum and winning bidder index are computed by the selected
global garbled circuit. The off-chain helper shown here only encodes the
already computed circuit output into canonical \texttt{outputBytes} and derives
the settlement anchor used by \(\mathrm{hOut}\)-binding checks.
\lstinputlisting[
  style=soliditysnippet,
  caption={Canonical packed output-bytes encoding and settlement-commitment hash derivation.},
  firstline=28,
  lastline=51
]{off-chain-common/src/settlement.rs}

\section{Demo Scenario Mapping}
\label{app:d2}
\begin{table}[htbp]
\centering
\begin{tabular}{|p{0.20\textwidth}|p{0.30\textwidth}|p{0.40\textwidth}|}
\hline
\textbf{Case} & \textbf{Deviation} & \textbf{Expected closure} \\ \hline
Case 1: honest run & no deviation & accepted settlement, assignment finalized, stage \texttt{Closed} \\ \hline
Case 2: defaulted buyer & buyer/evaluator misses OT/input-label commitment before the buyer-input deadline & default and slashing applied; run still reaches settlement and assignment \\ \hline
Case 3: garbler cheats & tampered opened-instance GC commitment/dispute mismatch & dispute succeeds; garbler slashed; contract closes without assignment \\ \hline
\end{tabular}
\caption{Scenario-to-outcome mapping used by the end-to-end demo harness.}
\label{tab:appendix-demo-cases}
\end{table}

\backmatter

\begin{aitools}
\textbf{Use of AI Tools in Thesis Preparation}

AI-based language models were used selectively as writing and editing assistants
during thesis preparation.
Their use was limited to drafting support, language refinement, structure
suggestions, and formatting assistance.

All technical concepts, protocol design decisions, implementation work,
experimental design, interpretation of results, and final conclusions were
developed and validated by the author.
AI tools were not used to autonomously design the protocol, conduct
experiments independently, make final methodological decisions, or replace
authorship.

All AI-generated suggestions were manually reviewed, edited, and verified
before inclusion in the manuscript.

Representative prompts (English) used in this process include:
\begin{itemize}
\item ``Rewrite the following paragraph into formal academic English.''
\item ``Improve grammar and clarity without changing technical meaning.''
\item ``Convert these bullet-point notes into a structured subsection.''
\item ``Suggest a chapter outline for a thesis on privacy-preserving auctions.''
\item ``Summarize the differences between commit-reveal and sealed-bid auctions.''
\item ``Improve transitions between these two paragraphs.''
\item ``Suggest clearer wording for the limitations section.''
\end{itemize}

All AI-assisted outputs were reviewed, revised, and adapted by the author
prior to inclusion.
\end{aitools}

\listoffigures
\cleardoublepage
\listoftables

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
